% Greek symbols
\newglossaryentry{euler_phi}
{
	name={$\phi$},
  	description={Roll euler angle. Also named \textit{Bank angle} in aviation},
  	sort=euler_phi
}

\newglossaryentry{euler_theta}
{
	name={$\theta$},
  	description={Pitch euler angle},
  	sort=euler_theta
}

\newglossaryentry{euler_psi}
{
	name={$\psi$},
  	description={Yaw euler angle. Also named \textit{Heading}},
	sort=euler_psi
}

\newglossaryentry{euler_attitude}
{
	name={$\Psi$},
	description={Attitude vector. $\Psi = [\phi \quad \theta \quad \psi]^T$},
	sort=euler_attitude
}

% Vectors
\newglossaryentry{r}
{
	name={$\bm{\mathrm{r}}$},
	description={Position vector $\bm{\mathrm{r}} = [x \quad y \quad z]^{T}$},
  	sort=r
}

\newglossaryentry{v}
{
	name={$\bm{\mathrm{v}}$},
	description={Velocity vector. $\bm{\mathrm{v}} = \bm{\mathrm{\dot{r}}} = [v_x \quad v_y \quad v_z]^T$},
	sort=v
}

\newglossaryentry{v_l}
{
	name={$\bm{\mathrm{v}}^\ell$},
	description={Velocity vector in local frame. $\bm{\mathrm{v}}^\ell = \bm{\mathrm{v}}_w^\ell + \bm{\mathrm{w}}^\ell$},
	sort=v_l
}

\newglossaryentry{v_wb}
{
	name={$\bm{\mathrm{v}}_w^b$},
	description={Relative airspeed velocity vector in body frame. $\bm{\mathrm{v}}_w^b = [u \quad v \quad w]^T$},
	sort=v_wb
}

\newglossaryentry{w_l}
{
	name={$\bm{\mathrm{w}}^\ell$},
	description={Wind velocity vector in local frame. $\bm{\mathrm{w}}^\ell = [w_N \quad w_E \quad w_D]^T$
				 Usually $w_D$ is assumed to be null},
	sort=w_l
}


\newglossaryentry{a}
{
	name={$\bm{\mathrm{a}}$},
	description={Acceleration vector. $\bm{\mathrm{a}} = \bm{\mathrm{\dot{v}}} = \bm{\mathrm{\ddot{r}}} = [a_x \quad a_y \quad a_z]^T$},
	sort=a
}

\newglossaryentry{wb}
{
	name={$\bm{\omega}^b$},
	description={Body rates vector. $\bm{\omega}^b = [p \quad q \quad r]^T$},
	sort=wb
}

\newglossaryentry{M_aerob}
{
	name={$\bm{\mathrm{M}}_{Aero}^b$},
	description={Body aerodynamic moments. $\bm{\mathrm{M}}_{Aero}^b = [\ell \quad m \quad n]^T$},
	sort=M_aerob
}

\newglossaryentry{M_Tb}
{
	name={$\bm{\mathrm{M}}_T^b$},
	description={Body thrust moments. $\bm{\mathrm{M}}_T^b = [\ell_T \quad m_T \quad n_T]^T$},
	sort=M_Tb
}

\newglossaryentry{F}
{
	name={$\bm{\mathrm{F}}$},
	description={Force vector. $\bm{\mathrm{F}} = [X \quad Y \quad Z]^T$},
	sort=F
}

\newglossaryentry{F_Aw}
{
	name={$\bm{\mathrm{F}}_{Aero}^w$},
	description={Aerodynamic forces in wind frame. \textit{Lift} $L$, \textit{drag} $D$ and \textit{cross-wind force} $C$. $\bm{\mathrm{F}}_{Aero}^w = [-D \quad -C \quad -L]^T$},
	sort=F_Aw
}

\newglossaryentry{F_Tb}
{
	name={$\bm{\mathrm{F}}_T^b$},
	description={Thrust force in body frame. $\bm{\mathrm{F}}_T^b = [X_T^b \quad Y_T^b \quad Z_T^b]^T$},
	sort=F_Tb
}

\newglossaryentry{gravity}
{
	name={$\bm{\mathrm{g}}$},
	description={Gravity vector},
	sort=gravity
}

\newglossaryentry{x_state}
{
	name={$\bm{\mathrm{x}}$},
	description={General state vector},
	sort=x_state
}

\newglossaryentry{quat}
{
	name={$\bm{\mathrm{\tilde{q}}}$},
	description={Hamiltonian attitude quaternion.
				 $\bm{\mathrm{\tilde{q}}} = (q_0, q_1, q_2, q_3) = (q_0, \bm{\mathrm{q}})$\\
				 A vector in the local NED frame $\ell$ can be represented in the body framae $b$ using
				 $\bm{\mathrm{\tilde{v}}}^b = \bm{\mathrm{\tilde{q}}} \, \bm{\mathrm{\tilde{v}}}^\ell \, \bm{\mathrm{\tilde{q}}}^*$ (or $\bm{\mathrm{\tilde{q}}}^{-1}$
				 instead of $\bm{\mathrm{\tilde{q}}}^*$ if $\bm{\mathrm{\tilde{q}}}$ is not unitary).\\
				 $\bm{\mathrm{\tilde{v}}}$ represents a \textit{quaternionized} vector: $\bm{\mathrm{\tilde{v}}} = (0,\bm{\mathrm{v}})$},
	sort=quat
}

% Matrices
\newglossaryentry{rot}
{
	name={$\bm{\mathrm{R}}_a^b$},
	description={Rotation matrix. Rotates a vector from frame $a$ to frame $b$. $\bm{\mathrm{v}}^b = \bm{\mathrm{R}}_a^b \bm{\mathrm{v}}^a$},
	sort=rot
}

% Scalars
\newglossaryentry{alpha}
{
	name={$\alpha$},
	description={Angle of attack (AOA)},
	sort=alpha
}

\newglossaryentry{beta}
{
	name={$\beta$},
	description={Angle of sideslip (AOS)},
	sort=beta
}

\newglossaryentry{control_surface}
{
	name={$\delta_{a,e,r}$},
	description={Aerodynamic control surface angular deflection. Subscripts $a$, $e$ and $r$ stand for \textit{aileron}, \textit{elevator} and \textit{rudder}, respectively. A positive deflection generates a negative moment},
	sort=control_surface
}

\newglossaryentry{chord}
{
	name={$c$},
	description={Wing chord length},
	sort=chord
}

\newglossaryentry{c_bar}
{
	name={$\bar{c}$},
	description={Mean aerodynamic chord (mac)},
	sort=c_bar
}

\newglossaryentry{wingspan}
{
	name={$b$},
	description={Wing span (from tip to tip)},
	sort=b_wingspan
}

\newglossaryentry{taper_ratio}
{
	name={$\lambda$},
	description={Taper ratio $\lambda = c_{tip}/c_{root}$},
	sort=taper_ratio
}

\newglossaryentry{aspect_ratio}
{
	name={$AR$},
	description={Aspect ratio. $AR = b^2/S$},
	sort=aspect_ratio
}

\newglossaryentry{sweep_angle}
{
	name={$\Lambda$},
	description={Leading-edge sweep angle},
	sort=sweep_angle
}

\newglossaryentry{mach}
{
	name={$M$},
	description={Mach number. Can be neglected for scale aircrafts},
	sort=mach
}


% Subscripts, superscripts and decorators
\newglossaryentry{hat}
{
	name={$\hat{()}$},
	description={Estimate},
	sort=hat,
	type=deco
}

\newglossaryentry{dot}
{
	name={$\dot{()}$},
	description={Time derivative},
	sort=dot,
	type=deco
}

\newglossaryentry{transpose}
{
	name={$()^T$},
	description={Matrix transpose},
	sort=transpose,
	type=deco
}

\newglossaryentry{inverse}
{
	name={$()^{-1}$},
	description={Matrix inverse},
	sort=transpose,
	type=deco
}

\newglossaryentry{frame_b}
{
	name={$()^b$},
	description={Resolved in the body FRD frame},
	sort=frame_b,
	type=deco
}

\newglossaryentry{frame_l}
{
	name={$()^\ell$},
	description={Resolved in the local NED frame},
	sort=frame_l,
	type=deco
}

\newglossaryentry{frame_w}
{
	name={$()^w$},
	description={Resolved in the wind frame},
	sort=frame_w,
	type=deco
}

\newglossaryentry{conj}
{
	name={$()^*$},
	description={Complex conjugate},
	sort=conj,
	type=deco
}

